Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-10-14 crowdsource/article.tex
Add second task
Decsribe method

\cite{sutera2014simple}

>>>>

A simple yet effective solution to the problem of connectome inference in
calcium imaging data consists of two steps. \cite{sutera2014simple} First,
processing the raw signals and to detect neural peak activities while filtering
noise. Second, inferring the degree of association between neurons from partial
correlation statistics, the inverse of the correlation matrix. This statitical
measure has the property to filter indirect associations between neuron and
gives a high degree of association between directly connected neurons. This
approach is the winning methods of the Connectomics challenge.

\section{Method}
\emph{A second mini-text I ask you will converge to the Methods section. Here I need
a more detailed presentation of your method. However, it has to be precise, but
still understandable for a biologist. A bit like a recipe in a cookbook for
beginners.}
